---
title: "Reproducible Biosurveillance with knitR"
fontsize: 10pt
date: Dec 8, 2015
output: beamer_presentation
        
---

# Motivation for using knitR
## Increase efficiency of own workflow

Don't have to jump back and forth between \newline

**Microsoft Word, Microsoft Excel, and R**

\vspace{5mm}

\begin{center}
\includegraphics{homer.jpg}
\end{center}

##Allows others to verify one's results

\begin{center}
\includegraphics{FarSide_RocketScientists.jpg}
\end{center}

\begin{center}
Everybody makes mistakes: reproducibility enables corrections.
\end{center}

##This was made with knitR
\begin{center}
\includegraphics{advancedR.jpg}
\end{center}


#Can create various outputs 
##PDF, Word, HTML, Beamer presentation

\begin{center}
\includegraphics{metadata.jpg}
\end{center}

For PDF...replace **beamer_presentation** with **pdf_document** \newline
For Word...replace **beamer_presentation** with **word_document**\newline
For HTML...replace **beamer_presentation** with **html_document**\newline

#Some RMarkdown syntax
##Have to create empy spaces and new lines
The
answer
is 
4.

$\;$
$\;$

The \newline
answer \newline
is \newline
4.\newline

##Embolden,italicize, change font color
**R is free**

$\;$
$\;$

*R is free*

$\;$
$\;$

\textcolor{red}{R is free}
        
#Embed R code
##Embed R code with chunks

```{r,}
bob=rnorm(100)
summary(bob)
```

##If you have chunks that take a long time to run

Put this below metadata section

\begin{center}
\includegraphics{chunks.jpg}
\end{center}

##Embed R code with inline expressions 
The number of days in a week multipled by the number of hours in a day: `r 7 * 24`

#Embed equations
## Place equation in a sentence
The number of days in a week multipled by the number of hours in a day: $z-score = \frac{x-\mu_x}{\sigma_x}$



##Make equation the star of a slide
$$z-score = \frac{x-\mu_x}{\sigma_x}$$

##For more complicated equations 

Download

http://www.lyx.org/

Create equation with point-and-click, convert to Latex, then paste in Rmd file

#Embed images
##Embed images
\begin{center}
\includegraphics{sas.jpg}
\end{center}

#Making tables
##Simple tables with the **printr** package
```{r }
library(printr)
options(digits = 4)
set.seed(123)
x = matrix(rnorm(40), 5)
x = as.data.frame(x)
x
```


##Modify table
```{r}
knitr::kable(x, digits = 2, caption = "A table produced by printr.")
```


##Just show output
```{r, echo=FALSE }
library(printr)
options(digits = 4)
set.seed(123)
x = matrix(rnorm(40), 5)
x = as.data.frame(x)
x
```



##Use Latex or Excel for more complicated tables
\begin{center}
\includegraphics{ComplexTable.jpg}
\end{center}

##If you choose the path of Latex
http://www.tablesgenerator.com/

#Compile directly from R scripts
##Compile directly from R scripts

rmarkdown::render("example.R","pdf_document")

#To learn more
## Visit this website
http://rmarkdown.rstudio.com/

## Download cheat sheet
http://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf

#Walk through some Rmd files that you can take home
##Walk through some Rmd files that you can take home
- R Markdown.Rmd (for this presentation)
- overview.Rmd
- Shiny_Intro.Rmd
